The globular cluster system of the Auriga simulations

### 2019-06-14 AurigaGCS.tex
Some minor rephrasings. Now only need to write discussion ...

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with catalogues
of observations of the Milky Way and Andromeda globular cluster populations available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. Furthermore we test whether any of the
Auriga galaxies has a metallicity and radial distribution that is consistent with
the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
the simulated and observed metallicities are drawn from the same distribution at
$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
the Andromeda galaxy. The same holds true for the distribution of galactocentric
radius. Overall, the Auriga simulations produce old star particles with higher
metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
would have to linearly decrease with increasing metallicity for the Auriga GC
candidates to be consistent with the MW GCS.
\end{abstract}

@@

An idea that has recently been studied in detail is the hypothesis that the physical 
processes responsible for the formation of young massive clusters \citep[YMCs, 
see][for a review]{2010ARA&A..48..431P}, observable in the local Universe in great
detail, also governs GC formation at high redshifts. In this framework, differences
between both classes of objects are caused by nearly a Hubble time of (dynamical)
evolution \citep[e.g.][]{1987degc.book.....S}. This picture is based on observed 
similarities between YMCs and GCs \citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W}
and strengthened by observations of gravitationally lensed objects at high redshifts
($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
GC progenitors at times of formation \citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}.
The modelling work by \citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} 
is now incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

Simulation resolutions have reached the mass range populated by GCs, and the
gravitational force softening can be as low several parsec. A number of groups 
can thus incorporate formation of (globular) star clusters into their 
high-resolution hydrodynamical cosmological zoom simulations. \citet{
2016ApJ...831..204R} run parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
\citet{2019MNRAS.482.4528E}.

@@

In this work we use state of the art simulations that produce realistic 
spiral galaxies at redshift zero that reproduce a number of observables. Therefore
the question naturally arises whether the simulations (also) yield a population 
of star particles that is consistent with the Milky Way and/or Andromeda globular 
cluster systems. In particular, we investigate the Auriga suite of cosmological 
zoom simulations (\citealt{2017MNRAS.467..179G}, and described in 
Sec.~\ref{sec:auriga}) which can serve as an ultimate test of the star formation 
model implemented in these simulations. The plan of the paper is as follows. We
summarise the relevant characteristics of the Auriga simulations in
section~\ref{sec:auriga}, followed by a summary of the observations of the
Milky Way (MW) and Andromeda globular cluster system (GCS) in
section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a
suite of high-resolution cosmological zoom simulations of Milky Way-mass
selected initial conditions. The simulations are performed with the
state-of-the art code \textsc{arepo} \citep{2010MNRAS.401..791S,
2016MNRAS.455.1134P}, that solves the magnetohydrodynamical equations on a
moving mesh, and an elaborate galaxy formation model that produces realistic
spiral galaxies at redshift $z=0$.

@@

The Auriga suite has a fiducial resolution level L4, accompanied by the lower
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
of the Auriga simulations is thus close to the characteristic peak mass of the
lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H},
although the gravitational softening is two orders of magnitudes larger than
typical GC radii. High-density gaseous regions are thus not expected to produce
surviving stellar clumps (GCs) with masses and radii consistent with GCs because
such objects would numerically disperse, even in the highest-resolution runs.
On the other hand, we can investigate (statistical) properties of age-selected
GC candidates because each star particle represents a single stellar population
with a total mass that could be consistent with one globular cluster.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
have since been discovered by various authors. The total confirmed number of GCs
in the MW adds up to 216 with new estimates now anticipating an additional thirty
GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\begin{itemize}
    \item The star formation model implemented in the Auriga simulations produces
    metallicity distributions that are more metal-rich the Milky Way and M31
    globular cluster systems.
    \item We reject the null hypothesis $H_0$ that MW (M31) and the GC candidates
    (all, insitu, and accreted) are drawn from the same underlying distribution
    for all Auriga L4 galaxies with $\geq 98.68$~\% confidence.
    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
    given our selection function of star particles selects all stars bound to the
    main subhalo in the main halo. The stellar mass is dominated by accreted star
    particles at radii beyond $20$~kpc The GCs in the MW and M31, on the other hand,
    have a much smaller radial extend.
    \item The cluster formation efficiency would have to increase with decreasing
    metallicity for GC candidates in the Auriga simulations to be consistent
    with the Milky Way GC system, given that we expect dynamical evolution to more strongly affect GC
    candidates at smaller radii.
    \item The Auriga simulations are not consistent with the picture that all
    metal-rich GCs formed insitu and that all metal-poor GCs were accreted.
\end{itemize}

@@

The analysis in this work was performed using the Python \citep{python}
programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
the Numpy \citep{2011CSE....13b..22V}, Scipy \citep{scipy}, and Astropy 
\citep{2013A&A...558A..33A} packages. Plots were generated using 
Matplotlib \citep{2007CSE.....9...90H}.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with catalogues
of observations of the Milky Way and Andromeda globular cluster populations available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. Furthermore we test whether any of the
Auriga galaxies has a metallicity and radial distribution that is consistent with
the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
the observed and simulated metallicities of GCs (GC candidates) are drawn from 
the same distribution at $\geq98.32$~\% confidence level, for the GCS of the 
Milky Way as well as that of the Andromeda galaxy. The same holds true for the 
distribution of galactocentric radius. Overall, the Auriga simulations produce 
old star particles with higher metallicities than the MW and M31 GCS and at 
larger radii. The formation efficiency would have to linearly decrease with 
increasing metallicity for the Auriga GC candidates to be consistent with the MW GCS.
\end{abstract}

@@

An idea that has recently been studied in detail is the hypothesis that the physical 
processes responsible for the formation of young massive clusters \citep[YMCs, 
see][for a review]{2010ARA&A..48..431P}, as observable in detail in the local 
Universe in great
, also governs GC formation at high redshifts. In this framework, differences
between both classes of objects are caused by nearly a Hubble time of (dynamical)
evolution \citep[e.g.][]{1987degc.book.....S}. This picture is based on observed 
similarities between YMCs and GCs \citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W}
and strengthened by observations of gravitationally lensed objects at high redshifts
($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
GC progenitors at times of formation \citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}.
The modelling work by \citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} 
is now incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

Simulation resolutions have reached the mass range populated by GCs, and the
gravitational force softening can be as low several parsec. A number of groups 
can thus incorporate formation of (globular) star clusters into their 
high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
run parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
\citet{2019MNRAS.482.4528E}.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies at redshift zero for which several global properties are consistent with 
the observations. The simulations yield realistic Milky Way analogues, and such
galaxies are known to host globular cluster systems. The question thus naturally 
arises whether the simulations (also) yield a population of star particles that 
is consistent with the Milky Way and/or Andromeda globular cluster systems. In 
particular, we investigate the Auriga suite of cosmological zoom simulations 
(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) because
a study of its GC system could serve as an ultimate test of the star formation 
model. The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
the observations of the Milky Way (MW) and Andromeda globular cluster system (GCS)
in section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a
suite of high-resolution cosmological zoom simulations of Milky Way-mass
selected initial conditions. The simulations are performed with the \textsc{arepo} 
\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} code that solves the 
magnetohydrodynamical equations on a moving mesh. The galaxy formation model 
produces realistic spiral galaxies at redshift $z=0$.

@@

The Auriga suite has a fiducial resolution level L4, accompanied by the lower
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
of the Auriga simulations is thus close to the characteristic peak mass of the
lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H},
although the gravitational softening is two orders of magnitudes larger than
typical GC radii. High-density gaseous regions are thus not expected to produce
surviving stellar clumps with masses and radii consistent with GCs because
such objects would numerically disperse, even in the highest-resolution runs.
On the other hand, we can investigate (statistical) properties of age-selected
GC candidates because each star particle represents a single stellar population
with a total mass that could be consistent with one globular cluster. This means
that their formation sites and that of a real-world GC may be consistent.

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\begin{itemize}
    \item The star formation model implemented in the Auriga simulations produces
    metallicity distributions that are more metal-rich the Milky Way and M31
    globular cluster systems.

    \item We reject the null hypothesis $H_0$ for any one of the Auriga simulations 
    that the GC candidates and the MW GCs are drawn from the same underlying 
    distribution with $\geq 98.68$~\% confidence. This statement holds true when
    we select all old star particles (GC candidates), but also when we select the 
    old accreted or the old in situ star particles. In addition, this is also
    the case when we test against the M31 GCS instead of the MW GCS.

    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
    given that our selection function of star particles selects all stars bound
    to the main subhalo in the main halo. The stellar mass is dominated by accreted 
    star particles at radii beyond $20$~kpc. The GCs in the MW and M31, on the 
    other hand, have a much smaller radial extend.

    \item The cluster formation efficiency would have to increase with decreasing
    metallicity for GC candidates in the Auriga simulations to be consistent
    with the Milky Way GC system, given that we expect dynamical evolution to 
    more strongly affect GC candidates at smaller radii. This trent of over-production
    of old star particles that are metal-rich and at large radii compared to 
    observed GCs is less clear for the M31 GCS.

    \item The Auriga simulations are not consistent with the picture that all
    metal-rich GCs formed insitu and that all metal-poor GCs were accreted.

\end{itemize}

@@

The analysis in this work was performed using the Python \citep{python}
programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
\citep{2013A&A...558A..33A} packages. Plots were created with
Matplotlib \citep{2007CSE.....9...90H}.
